Methods and Results

### 2022-10-15 ms.Rmd
Fixed a few small size issues and re-export figs

p4 <- (p1 + (p2 / p3)) + plot_annotation(tag_levels = "A", tag_suffix = ")")
p4
ggsave(plot = p4, filename = "fig1.png", width = 12, height= 5, path = "./output/figs", units = "in", device="png", dpi = 600)
ggsave(plot = p4, filename = "fig1.pdf", path = "./output/figs", height = 7, width = 10, device = "pdf")

@@

ggsave(plot = plot, filename = "fig2.png", path = "./output/figs", height = 7.4, width = 20.8, device = "png", dpi = 600)
ggsave(plot = plot, filename = "fig2.pdf", path = "./output/figs", height = 7, width = 10, device = "pdf")
plot
```

>>>>

p4 <- (p1 + (p2 / p3)) + plot_annotation(tag_levels = "A", tag_suffix = ")")
p4
ggsave(plot = p4, filename = "fig1.png", width = 12, height= 5, path = "./output/figs", units = "in", device="png", dpi = 600)
ggsave(plot = p4, filename = "fig1.pdf", path = "./output/figs", height = 5, width = 12, device = "pdf")

@@

ggsave(plot = plot, filename = "fig2.png", path = "./output/figs", height = 7.4, width = 20.8, device = "png", dpi = 600)
ggsave(plot = plot, filename = "fig2.pdf", path = "./output/figs", height = 7.4, width = 20.8, device = "pdf")
plot
```
